TacticToe: Learning the Game of Tactics

### 2018-02-19 tactictoe_jv.tex
minor

\begin{itemize}
\item Proof recording at the tactic level is made more precise. Pattern
matching constructions, opening of submodules are supported. The different
recording steps (parsing, unfolding and replaying) are regrouped into a single
\sml function.
\item Monte Carlo tree search~~\cite{montecarlo} (MCTS) replaces A* as our
search algorithm. The MCTS algorithm gives a more balanced feedback on
the success of
each proof step by
comparing subtrees of the search tree instead of leafs. The policy and
evaluation are learned
through supervised learning.
\item Proof guidance required by MCTS is given by predictors for
three kinds of objects: tactics, theorems and lists of goals.
\item The orthogonalization process that eliminates redundant tactics is
formally described.
\item A tactic abstraction method is introduced. It enables us to create
more general and flexible tactics where tactic arguments are dynamically
predicted.
\item The internal ATP \metis is complemented
by asynchronous calls to \eprover to help \tactictoe during proof search.
\item Evaluation of \tactictoe success rate relative to
the length of the original proofs.
\item User interaction is enhanced by the minimization and prettification
applied on the generated proof.
\end{itemize}

>>>>

\begin{itemize}
\item Proof recording at the tactic level is made more precise. Pattern
matching constructions, opening of submodules are supported. The different
recording steps (parsing, unfolding and replaying) are regrouped into a single
\sml function.
\item Monte Carlo tree search~~\cite{montecarlo} (MCTS) replaces A* as our
search algorithm. The MCTS algorithm gives a more balanced feedback on
the success of
each proof step by
comparing subtrees of the search tree instead of leafs. The policy and
evaluation are learned
through supervised learning.
\item Proof guidance required by MCTS is given by predictors for
three kinds of objects: tactics, theorems and lists of goals.
\item The orthogonalization process that eliminates redundant tactics is 
described in a precise manner.
\item A tactic abstraction mechanism is introduced. It enables us to create
more general and flexible tactics where tactic arguments are dynamically
predicted.
\item The internal ATP \metis is complemented
by asynchronous calls to \eprover to help \tactictoe during proof search.
\item First evaluation of \tactictoe success rate relative to
the length of the original human proofs.
\item Minimization and prettification of the generated proof improves user 
interaction.
\end{itemize}
